
---
title: '**Task Level analysis for Sunrun Completed projects**'
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 2
  pdf_document:
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_depth: 2
  word_document: default
---

```{r,  echo  =  FALSE,  results  =  'hide',  message  =  FALSE,  warning  =  FALSE}
#loading the libraries
library(plyr)  ;  library(sqldf)  ;  library(ggplot2)  ;  library(tcltk2)
library(lubridate)  ;  library(bizdays)  ;  library(plotly)  ;  library(ade4)
library(reshape2)  ;  library(rCharts)  ;  library(clickme)  ;  library(knitr) #The package
setwd("~/Desktop/courses/PAST/Practicum1/Datasets/Sunrun/")
#laoding the datasets
Project_milestone  <-  read.csv("WFM_Project_Milestone_Dates.csv")  
Project_Attributes  <-  read.csv("Project_Attributes copy.csv")
Project_Attributes  <-  Project_Attributes[  ,  -c(15:16)]
#---------------------#--------------------#---------------------#---------------------
#-----------------#  Preparing the dataset #---------------------#---------------------
#---------------------#--------------------#---------------------#---------------------
#Creating aliases
PM  <-  Project_milestone  ;  PA  <-  Project_Attributes  
rm(Project_Attributes,  Project_milestone)
#removing duplicates from both the dataset
PM  <-  PM[!duplicated(PM$Project.Name), ]  ;  PA  <-  PA[!duplicated(PA$Project.Name), ]   
#changing to suitable names
names(PA)  <-  c("Project.Name","Status","Purchased.through","Contract.type",
"Install.Branch","Utility","jurisdiction","Muncipality","System.size","If_build",
"if_MPU","If_Re_roof","If_HOA","If_PEStamp")
#Completion dates data
WC  <-  read.csv("WFM_Completion_Dates.csv")
attach(WC)  
data  <-  WC[,c("Phase.Name",  "Workflow.Task.Name")]
names(data)  <-  c("Phase",  "Task")  ;  detach(WC)
#aggregating the bad.data to clean it
data.1  <-  sqldf("select Task,  Phase,  count(*) cnt from data group by Task,  Phase")
data.2  <-  data.1[order(-data.1$cnt),  ]#descending order, Task
#removing misclassified tasks out
data.3  <-  data.2[!duplicated(data.2$Task), ]  
#removing "Tasks" with too little counts (less than equal to 500 steps)
data.4  <-  data.3[data.3$cnt  >  500,  ]
data.4  <-  data.4[,  -3]
#total counts lost as percentage
sum(data.3$cnt[data.3$cnt  <=  500])  *  100 /  sum(data.3$cnt) #4.2% thats okay
#mapping the resulatant to the original dataset
names(WC)[2 : 3]  <-  c("old.Phase",  "Task")
#join using the "plyr" package
good.WC   <-  join(WC,  data.4,  by = "Task",  type  =  "inner",  match  =  "all")
#Using the correct phase information
good.WC  <-  good.WC[  ,  -c(2,  6)]
#Correcting column names
good.WC$Phase  <-  as.character(good.WC$Phase)
good.WC$Phase[good.WC$Phase  ==  "Project Initiation"]  <-  "1. Initiation"
good.WC$Phase[good.WC$Phase  ==  "Site Audit"]  <-  "2. Audit"
good.WC$Phase[good.WC$Phase  ==  "Contract Approval"]  <-  "3. Approval"
good.WC$Phase[good.WC$Phase  ==  "Design"]  <-  "4. Design"
good.WC$Phase[good.WC$Phase  ==  "Pre-Installation Approvals"]  <-  "5. Pre-Installation"
good.WC$Phase[good.WC$Phase  ==  "Installation"]  <-  "6. Installation"
good.WC$Phase[good.WC$Phase  ==  "Completion"]  <-  "7. Completion"
#Treating dates
good.WC$Start.Date  <-  as.Date(good.WC$Start.Date,  format = "%m/%d/%y %H:%M")
good.WC$End.Date  <-  as.Date(good.WC$End.Date,  format = "%m/%d/%y %H:%M")
#Excluding Holidays & Sundays
cal  <-  Calendar(holidaysANBIMA,  weekdays  =  'sunday')
#Days with Both Start Dates & End dates
good.WC  <-  good.WC[!is.na(good.WC$Task),]
#Goodsubset
good.WC  <-  good.WC[good.WC$Start.Date  >=  '2015-06-15',]
data  <-  good.WC[!is.na(good.WC$Start.Date)  &  !is.na(good.WC$End.Date),  ]
#Days with Start Dates less than Equal to End dates
data.new  <-  data[data$Start.Date  <=  data$End.Date,  ]
data.new$day.diff  <-  bizdays(data.new$Start.Date,  data.new$End.Date,  cal)
data.new  <-  data.new[data.new$Start.Date  >=  '2015-06-15',]
#Joining with the Project Attributes table to Get Project level details
complete.data  <-  join(data.new,  PA,  by  =  "Project.Name"
                        ,  type  =  "inner",  match  =  "all") 
#selecting important variables from PM
PM.1  <-  PM[,c(1,3,35)]  ;  names(PM.1)[2:3]  <-  c("Start",  "End")
PM.1$Start  <-  as.Date(PM.1$Start,  format  =  "%m/%d/%y %H:%M")
PM.1$End  <-  as.Date(PM.1$End,  format  =  "%m/%d/%y")
PM.1  <-  na.omit(PM.1)  
PM.1$End[PM.1$Start  >  PM.1$End]  <-  "2015-11-03" #For dates with no End Dates
PM.1$day.diff  <-  bizdays(PM.1$Start,  PM.1$End,  cal)
#Now getting to the PA dataset
#Take only those projects that have been started after 14th June
PA  <-  merge(PA,  data.new,  by  =   "Project.Name")[1:14]
PA  <-  unique(PA)  
PA  <-  merge(PA,  PM.1,  by  =   "Project.Name")
#Eliminate all entries with Start Dates less than 15th June, to mantain the accuracy 
PA  <-  PA[PA$Start>"2015-06-14",]  
PA  <-  PA[,-c(15:16)]
#Treating False values in IF_HOA column
PA$If_HOA[PA$If_HOA  ==  2]  <-  1  
PA$If_HOA[is.na(PA$If_HOA)]  <-  0
#Ensuring that the Task level data only contains the completed Projects Jun-15 to 2nd Nov
complete.data  <-  merge(complete.data,  PA,  by  =  "Project.Name")[,c(2,6,8,9:19)]
#Changing the names of the complete data
names(complete.data)  <-  c("Task","Time","Purchased","Contract","Install_Branch"
    ,"Utility","Jusrisdiction","Muncipality","Size","IF_Build","IF_MPU","IF_Reroof"
    ,"IF_HOA","IF_PE")
CD  <-  complete.data #renaming
#Subsetting for only Tasks with a reasonable frequency
rm(list  =  ls()[!(ls()  %in%  'CD')]) #Cleaning the memory
#plotly styling
f1  <-  list(family  =  "Arial, sans-serif",  size  =  20,  color  =  "brown")
f2  <-  list(family  =  "Arial, sans-serif",  size  =  16,  color  =  "blue")
m  <-  list( l  =  50,  r  =  50,  b  =  50,  t  =  50,  pad  =  4) #Setting margin
#Clubbing Few Tasks Together
CD$Task[CD$Task  == "Schedule Installation (B)"]  <-  "Schedule Installation"
CD$Task[CD$Task  == "Schedule Installation (C)"]  <-  "Schedule Installation"
CD$Task[CD$Task  == "Schedule Installation (E)"]  <-  "Schedule Installation"
CD$Task[CD$Task  == "Submit Final Interconnection (A)"]  <-  "Submit Final Interconnection"
CD$Task[CD$Task  == "Submit Rebate Application (A)"]  <-  "Submit Rebate Application"
CD$Task[CD$Task  == "Request NTP (B)"]  <-  "Request NTP"
CD$Task[CD$Task  == "Receive Final Rebate Claim With Customer Signature (A)"]  <-  "Receive Final Rebate Claim With Customer Signature"
CD$Task[CD$Task  == "Permitting Blocked, Project Needs Review"]  <-  "Projects Need Review"
CD$Time[CD$Time  <  0]  <-  0 #cleaning bad entries
```

************
```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
Task.mean  <-  aggregate(CD$Time,  by  =  list(CD$Task),  mean)
names(Task.mean)  <-  c("Task","Mean_Time")
Task.sd  <-  aggregate(CD$Time,  by  =  list(CD$Task),  sd)
names(Task.sd)  <-  c("Task","Sd_Time")
Task.data  <-  merge(CD[,c(1,2)],  Task.mean,  by  =  "Task")
Task.data  <-  merge(Task.data,  Task.sd,  by  =  "Task")
Task.data$nor  <-  (Task.data$Time  -  Task.data$Mean_Time)/Task.data$Sd_Time
Task.freq  <-  aggregate(CD$Task,  by  =  list(CD$Task),  length)
names(Task.freq)  <-  c("Task","Freq")

Task.freq  <-  Task.freq[order(-Task.freq$Freq),  ] #Freq
Task.freq$Categ  <-  NULL #Assigning a category to these tasks based on Frequency
Task.freq$Categ[Task.freq$Freq  >  2000]  <-  "High Freq"
Task.freq$Categ[Task.freq$Freq  <=  2000  &  Task.freq$Freq  >  400]  <-  "Mid Freq"
Task.freq$Categ[Task.freq$Freq  <=  400]  <-  "Low Freq"
CD  <-  merge(CD,  Task.freq,  by  =  "Task")
CD  <-  CD[,  -15]

#Box plot for the data
a1  <-  list(title  =  'Task',  titlefont  =  f1,  showticklabels  =  TRUE,
             tickangle  =  35,  tickfont  =  f2,  autorange  =  "reversed")
a2  <-  list(title  =  "Average Days",  titlefont  =  f1)
m  <-  list(l  =  50,  r  =  200,  b  =  250,  t  =  25,  pad  =  8)
```

#Statistics on each of the tasks based on their frequency

***************
##Time taken by tasks of high penetration (>90% Projects)

```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#Most Frequent Tasks
plot_ly(CD[CD$Categ  ==  "High Freq",  ],  x  =  Task,  name  =  title,  y  =  Time
,  type  =  "box") %>% layout(xaxis  =  a1,  yaxis  =  a2,  showlegend  =  FALSE
,  margin  = m) %>% layout(autosize  =  F,  width  =  1000,  height  =  500)
```

***************
##Time taken by tasks of medium penetration ([20-90]% Projects)

```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#Mid Frequent Tasks
plot_ly(CD[CD$Categ  ==  "Mid Freq",  ],  x  =  Task, name  =  title,  y  =  Time
,  type  =  "box") %>% layout(xaxis  =  a1,  yaxis  =  a2,  showlegend  =  FALSE
,  margin  = m) %>% layout(autosize  =  F,  width  =  1000,  height  =  500)
```

***************
##Time taken by tasks of low penetration (<20% Projects)

```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#Least Frequent Tasks
plot_ly(CD[CD$Categ  ==   "Low Freq",  ],  x  =  Task, name  =  title,  y  =  Time
,  type  =  "box") %>% layout(xaxis  =  a1,  yaxis  =  a2,  showlegend  =  FALSE
,  margin  = m) %>% layout(autosize  =  F,  width  =  1000,  height  =  500)
```

****************
#Binary factors on Top 10 Tasks

```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
a1  <-  list(title  =  'Task',  titlefont  =  f1,  showticklabels  =  TRUE,
             tickangle  =  45,  tickfont  =  f2,  autorange  =  "reversed")
a2  <-  list(title  =  "Average Days",  titlefont  =  f1)
m  <-  list(l  =  50,  r  =  200,  b  =  300,  t  =  25,  pad  =  8)
all.factors  <-  names(CD)[10:14] #Factors,  Number of Tasks
```

##Impact of Build Partner

```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#Function to pick n most influenced tasks by individual factors
cols  <-  c(all.factors[1],"Time","Task")
plot  <-  CD[,  cols]
data  <-  aggregate(plot$Time,  by  =  list(plot[,  all.factors[1]],  plot$Task),  mean)
names(data)[1:2]  <-  c("var","Task")
data1  <-  data[data$var  ==  1,  c(2,3)]  ;  data0  <-  data[data$var  ==  0,  c(2,3)]
data2  <-  merge(data1,  data0,  by  =  'Task')  ;  data2$ratio  <-  data2$x.x/data2$x.y
data2  <-  data2[order(-data2$ratio),  ]#Sorting the dataframe on Inlluence ratio
data2  <-  data2[1:10,  c(1:3)] #10 rows of First 3 cols
names(data2)  <-  c("Task",  "With",  "Without") #With & Without factor
data3  <- reshape(data2,  varying  =  c("With", "Without"),  v.names  =  "Time"
,  timevar  =  "Factor",  times  =  c("With", "Without"),  direction  =  "long")
plot_ly(data  =  data3,  x  =  Task,  y  =  Time,  type  =  "bar"
,  color  =  Factor)  %>% layout(xaxis  =  a1,  yaxis  =  a2
,  margin  =  m)  %>%  layout(autosize  =  F,  width  =  1000,  height  =  500)
```

****************
##Impact of MPU
```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#Function to pick n most influenced tasks by individual factors
cols  <-  c(all.factors[2],"Time","Task")
plot  <-  CD[,  cols]
data  <-  aggregate(plot$Time,  by  =  list(plot[,  all.factors[2]],  plot$Task),  mean)
names(data)[1:2]  <-  c("var","Task")
data1  <-  data[data$var  ==  1,  c(2,3)]  ;  data0  <-  data[data$var  ==  0,  c(2,3)]
data2  <-  merge(data1,  data0,  by  =  'Task')  ;  data2$ratio  <-  data2$x.x/data2$x.y
data2  <-  data2[order(- data2$ratio),  ]#Sorting the dataframe on Inlluence ratio
data2  <-  data2[1:10,  c(1:3)] #n rows of First 3 cols
names(data2)  <-  c("Task",  "With",  "Without") #With & Without factor
data3  <- reshape(data2,  varying  =  c("With", "Without"),  v.names  =  "Time"
,  timevar  =  "Factor",  times  =  c("With", "Without"),  direction  =  "long")
plot_ly(data  =  data3,  x  =  Task,  y  =  Time,  type  =  "bar"
,  color  =  Factor)  %>% layout(xaxis  =  a1,  yaxis  =  a2
,  margin  =  m)  %>%  layout(autosize  =  F,  width  =  1000,  height  =  500)
```

****************

##Impact of Re-Roofing

```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#Function to pick n most influenced tasks by individual factors
cols  <-  c(all.factors[3],"Time","Task")
plot  <-  CD[,  cols]
data  <-  aggregate(plot$Time,  by  =  list(plot[,  all.factors[3]],  plot$Task),  mean)
names(data)[1:2]  <-  c("var","Task")
data1  <-  data[data$var  ==  1,  c(2,3)]  ;  data0  <-  data[data$var  ==  0,  c(2,3)]
data2  <-  merge(data1,  data0,  by  =  'Task')  ;  data2$ratio  <-  data2$x.x/data2$x.y
data2  <-  data2[order(- data2$ratio),  ]#Sorting the dataframe on Inlluence ratio
data2  <-  data2[1:10,  c(1:3)] #n rows of First 3 cols
names(data2)  <-  c("Task",  "With",  "Without") #With & Without factor
data3  <- reshape(data2,  varying  =  c("With", "Without"),  v.names  =  "Time"
,  timevar  =  "Factor",  times  =  c("With", "Without"),  direction  =  "long")
plot_ly(data  =  data3,  x  =  Task,  y  =  Time,  type  =  "bar"
,  color  =  Factor)  %>% layout(xaxis  =  a1,  yaxis  =  a2
,  margin  =  m)  %>%  layout(autosize  =  F,  width  =  1000,  height  =  500)
```

****************

##Impact of HOA

```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#Function to pick n most influenced tasks by individual factors
cols  <-  c(all.factors[4],"Time","Task")
plot  <-  CD[,  cols]
data  <-  aggregate(plot$Time,  by  =  list(plot[,  all.factors[4]],  plot$Task),  mean)
names(data)[1:2]  <-  c("var","Task")
data1  <-  data[data$var  ==  1,  c(2,3)]  ;  data0  <-  data[data$var  ==  0,  c(2,3)]
data2  <-  merge(data1,  data0,  by  =  'Task')  ;  data2$ratio  <-  data2$x.x/data2$x.y
data2  <-  data2[order(- data2$ratio),  ]#Sorting the dataframe on Inlluence ratio
data2  <-  data2[1:10,  c(1:3)] #n rows of First 3 cols
names(data2)  <-  c("Task",  "With",  "Without") #With & Without factor
data3  <- reshape(data2,  varying  =  c("With", "Without"),  v.names  =  "Time"
,  timevar  =  "Factor",  times  =  c("With", "Without"),  direction  =  "long")
plot_ly(data  =  data3,  x  =  Task,  y  =  Time,  type  =  "bar"
,  color  =  Factor)  %>% layout(xaxis  =  a1,  yaxis  =  a2
,  margin  =  m)  %>%  layout(autosize  =  F,  width  =  1000,  height  =  500)
```

****************

##Impact of Professional Engineer

```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#Function to pick n most influenced tasks by individual factors
cols  <-  c(all.factors[5],"Time","Task")
plot  <-  CD[,  cols]
data  <-  aggregate(plot$Time,  by  =  list(plot[,  all.factors[5]],  plot$Task),  mean)
names(data)[1:2]  <-  c("var","Task")
data1  <-  data[data$var  ==  1,  c(2,3)]  ;  data0  <-  data[data$var  ==  0,  c(2,3)]
data2  <-  merge(data1,  data0,  by  =  'Task')  ;  data2$ratio  <-  data2$x.x/data2$x.y
data2  <-  data2[order(- data2$ratio),  ]#Sorting the dataframe on Inlluence ratio
data2  <-  data2[1:10,  c(1:3)] #n rows of First 3 cols
names(data2)  <-  c("Task",  "With",  "Without") #With & Without factor
data3  <- reshape(data2,  varying  =  c("With", "Without"),  v.names  =  "Time"
,  timevar  =  "Factor",  times  =  c("With", "Without"),  direction  =  "long")
plot_ly(data  =  data3,  x  =  Task,  y  =  Time,  type  =  "bar"
,  color  =  Factor)  %>% layout(xaxis  =  a1,  yaxis  =  a2
,  margin  =  m)  %>%  layout(autosize  =  F,  width  =  1000,  height  =  500)
```

************
# Categorical factors on Top 10 Tasks

```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
a1  <-  list(title  =  'Task',  titlefont  =  f1,  showticklabels  =  TRUE,
             tickangle  =  45,  tickfont  =  f2,  autorange  =  "reversed")
a2  <-  list(title  =  "Average Days",  titlefont  =  f1)
m  <-  list(l  =  50,  r  =  200,  b  =  300,  t  =  25,  pad  =  8)
```

##Contract wise spread of task time
```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#variations at Contract Type
main.task  <-  aggregate(CD$Time,  by  =  list(CD$Task),  mean)
names(main.task)  <-  c("Task","Time")
main.task  <-  main.task[order(-main.task$Time),  ][1:10,  ]
#Pulling the data from the main set for categoricals
cols  <-  c("Contract","Time","Task")
data1  <-  CD[,  cols]  ;  names(data1)[1]  <-  "Factor"
#Choosing only top 10 Categorical levels by frequency
small.task  <-  data.frame(table(CD[, "Contract"]))
names(small.task)  <-  c("Factor","Freq")
small.task  <-  small.task[order(-small.task$Freq),  ][1:5,  ]  
good.data  <-  merge(data1,  small.task,  by  =  "Factor")[,1:3]
good.data  <-  merge(good.data,  main.task,  by  =  "Task")[,1:3] 
data.1  <-  unique(good.data[,c(1,2)])
d  <-  aggregate(data.1$Task,  by  =  list(data.1$Task),  length)  ;  names(d)  <-  c("Task","cnt")
good.data  <-  merge(good.data,  d,  by  =  "Task")[,1:4] 
good.data  <-  good.data[order(-good.data$cnt), ]  ;  good.data  <-  good.data[,  -4]
#Plotting the same on a facet_wrap
plot_ly(good.data,  x  =  Task,  y  =  Time.x,  color  =  Factor
,  type  =  "box")  %>%  layout( xaxis  =  a1,  yaxis  =  a2,  margin  =  m
,  boxmode  =  "group",  legend  =  list(x  =  1
,  y  =  1))  %>%  layout(autosize  =  F,  width  =  1000,  height  =  500)
```
*********************

##Installation Branch wise spread of task time 
```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#variations at Install Branch type
main.task  <-  aggregate(CD$Time,  by  =  list(CD$Task),  mean)
names(main.task)  <-  c("Task","Time")
main.task  <-  main.task[order(-main.task$Time),  ][1:10,  ]
#Pulling the data from the main set for categoricals
cols  <-  c("Install_Branch","Time","Task")
data1  <-  CD[,  cols]  ;  names(data1)[1]  <-  "Factor"
#Choosing only top 10 Categorical levels by frequency
small.task  <-  data.frame(table(CD[, "Install_Branch"]))
names(small.task)  <-  c("Factor","Freq")
small.task  <-  small.task[order(-small.task$Freq),  ][1:5,  ]  
good.data  <-  merge(data1,  small.task,  by  =  "Factor")[,1:3]
good.data  <-  merge(good.data,  main.task,  by  =  "Task")[,1:3] 
data.1  <-  unique(good.data[,c(1,2)])
d  <-  aggregate(data.1$Task,  by  =  list(data.1$Task),  length) 
names(d)  <-  c("Task","cnt")
good.data  <-  merge(good.data,  d,  by  =  "Task")[,1:4] 
good.data  <-  good.data[order(good.data$cnt), ]  ;  good.data  <-  good.data[,  -4]
#Plotting the same on a facet_wrap
plot_ly(good.data,  x  =  Task,  y  =  Time.x,  color  =  Factor
,  type  =  "box")  %>%  layout(xaxis  =  a1,  yaxis  =  a2 
,  margin  =  m,  boxmode  =  "group",  legend  =  list(x  =  1
,  y  =  1))  %>%  layout(autosize  =  F,  width  =  1000,  height  =  500)
```

*********************

##Utility wise spread of task time 
```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#variations at Utility type
main.task  <-  aggregate(CD$Time,  by  =  list(CD$Task),  mean)
names(main.task)  <-  c("Task","Time")
main.task  <-  main.task[order(-main.task$Time),  ][1:10,  ]
#Pulling the data from the main set for categoricals
cols  <-  c("Utility","Time","Task")
data1  <-  CD[,  cols]  ;  names(data1)[1]  <-  "Factor"
#Choosing only top 10 Categorical levels by frequency
small.task  <-  data.frame(table(CD[, "Utility"]))
names(small.task)  <-  c("Factor","Freq")
small.task  <-  small.task[order(-small.task$Freq),  ][1:5,  ]  
good.data  <-  merge(data1,  small.task,  by  =  "Factor")[,1:3]
good.data  <-  merge(good.data,  main.task,  by  =  "Task")[,1:3] 
data.1  <-  unique(good.data[,c(1,2)])
d  <-  aggregate(data.1$Task,  by  =  list(data.1$Task),  length)  ;  names(d)  <-  c("Task","cnt")
good.data  <-  merge(good.data,  d,  by  =  "Task")[,1:4] 
good.data  <-  good.data[order(good.data$cnt), ]  ;  good.data  <-  good.data[,  -4]
#Plotting the same on a facet_wrap
plot_ly(good.data,  x  =  Task,  y  =  Time.x,  color  =  Factor
,  type  =  "box")  %>%  layout(xaxis  =  a1,  yaxis  =  a2 
,  margin  =  m,  boxmode  =  "group",  legend  =  list(x  =  1
,  y  =  1))  %>%  layout(autosize  =  F,  width  =  1000,  height  =  500)
```

*********************

##Jurisdiction wise spread of task time
```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#variations at Jurisdiction type
main.task  <-  aggregate(CD$Time,  by  =  list(CD$Task),  mean)
names(main.task)  <-  c("Task","Time")
main.task  <-  main.task[order(-main.task$Time),  ][1:10,  ]
#Pulling the data from the main set for categoricals
cols  <-  c("Jusrisdiction","Time","Task")
data1  <-  CD[,  cols]  ;  names(data1)[1]  <-  "Factor"
#Choosing only top 10 Categorical levels by frequency
small.task  <-  data.frame(table(CD[, "Jusrisdiction"]))
names(small.task)  <-  c("Factor","Freq")
small.task  <-  small.task[order(-small.task$Freq),  ][1:5,  ]  
good.data  <-  merge(data1,  small.task,  by  =  "Factor")[,1:3]
good.data  <-  merge(good.data,  main.task,  by  =  "Task")[,1:3] 
data.1  <-  unique(good.data[,c(1,2)])
d  <-  aggregate(data.1$Task,  by  =  list(data.1$Task),  length)  ;  names(d)  <-  c("Task","cnt")
good.data  <-  merge(good.data,  d,  by  =  "Task")[,1:4] 
good.data  <-  good.data[order(-good.data$cnt), ]  ;  good.data  <-  good.data[,  -4]
#Plotting the same on a facet_wrap
plot_ly(good.data,  x  =  Task,  y  =  Time.x,  color  =  Factor
,  type  =  "box")  %>%  layout(xaxis  =  a1,  yaxis  =  a2,  margin  =  m
,  boxmode  =  "group",  legend  =  list(x  =  1
,  y  =  1))  %>%  layout(autosize  =  F,  width  =  1000,  height  =  500)
```
*********************


```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#---------------------#--------------------#---------------------#---------------------
#-----------------#  Clearing the environment ----#---------------------
#---------------------#--------------------#---------------------#---------------------
#unloading all the packages
detach("package:sqldf",  unload  =  TRUE)
detach("package:lubridate",  unload  =  TRUE)
detach("package:bizdays",  unload  =  TRUE)
detach("package:rCharts",  unload  =  TRUE)
detach("package:clickme",  unload  =  TRUE)
detach("package:plotly",  unload  =  TRUE)
detach("package:ggplot2",  unload  =  TRUE)
detach("package:tcltk2",  unload  =  TRUE)
detach("package:plyr",  unload  =  TRUE)
detach("package:ade4",  unload  =  TRUE)
#Removing all the objects too
rm(list  =  ls())
```
