---
title: '**Tracking User activities on Adds with interactive dashboards**'
author: "Abhishek"
date: "March 26, 2016"
output:
  html_document:
    toc: yes
  pdf_document:
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_depth: 2
  word_document: default
---

```{r,  echo  =  FALSE,  results  =  'hide',  message  =  FALSE,  warning  =  FALSE}
#-------------#-------------# Setting the environment #-------------#-------------#
#Loading the libraries
library(plotly)  ;  library(Hmisc)  ;  library(doMC) #For Multithreading
registerDoMC()#Multithreading
setwd('~/Desktop/courses/PAST/Interview_Skills/Sharethrough/')#The path

#loading the datasets
MPCDE  <-  read.csv('str-data-challenge-mpcde.csv',  header  =  T)
PC  <-  read.csv('str-data-challenge-pc.csv',  header  =  T)
PL  <-  read.csv('str-data-challenge-pl.csv',  header  =  T)

summary(MPCDE)  ;  dim(MPCDE)  ;  str(MPCDE)#Basic exploration of the datasets
cat("Table MPCDE: Performance of each add across different cuts")

table(MPCDE$FIFTEEN_SECOND_VIEWS) #All NULLS
table(MPCDE$THIRTY_SECOND_VIEWS) #All NULLS

#Since the last 2 columns of MPCDE are all NULLs lets exclude them
#Since the Date is held constant, lets exclude that too
MPCDE  <-  MPCDE[,  -c(1,21:22)]

#Renaming the column in PL dataframe to the more accepted 'PLACEMENT_KEY'
names(PL)[1]  <-  "PLACEMENT_KEY"

#Now counting number of the common variable "PLACEMENT_KEY" for the 3 datasets
length(unique(PL$PLACEMENT_KEY))  #4665
length(unique(PC$PLACEMENT_KEY))  #5365
length(unique(MPCDE$PLACEMENT_KEY))  #1546

#framing a bigger dataset
big.data  <-  merge(MPCDE,  PL,  by  =  "PLACEMENT_KEY",  all.x  =  T)
rm(MPCDE,  PL,  PC)

#Adding a column for all the views & shares
big.data$ViewsplusShares  <-  apply(big.data[,  c(11:18)],  1,  sum)

big.data  <-  big.data[,  -c(11:19)]#getting rid of the superflous columns

#plotly styling
f1  <-  list(family  =  "Arial, sans-serif",  size  =  16,  color  =  "Green")
f2  <-  list(family  =  "Arial, sans-serif",  size  =  12,  color  =  "Brown")
m  <-  list(l  =  100,  r  =  100,  b  =  100,  t  =  25,  pad  =  16) #Setting margin
```

# (Views + Shares) 
```
We have added up all the shares & Views from columns, namely:
  1.  Twitter shares
  2.  Facebook shares
  3.  Vine shares
  4.  Custom shares
  5.  Email shares
  6.  Three second views
  7.  Auto play views
  8.  Video plays
  
to create a new column 'Views + Shares' for our analysis. This is a collective measure of a 
user's digital activity on the add.
```

*******************
#Country wise click rate percentage (clicks/visible impressions) conditioned on Brand Guarantee (BG)
```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
data.1a  <-  aggregate(big.data$CLICKS,  by  =  list(big.data$COUNTRY
                                      ,  big.data$GUARANTEED_BRAND_SAFE),  sum)
data.1b  <-  aggregate(big.data$VISIBLE_IMPRESSIONS
            ,  by  =  list(big.data$COUNTRY,  big.data$GUARANTEED_BRAND_SAFE),  sum)
data.1  <-  merge(data.1a,  data.1b,  by  =  c("Group.1","Group.2"))
names(data.1)  <-  c("Country",  "Brand_Guarantee",  "Clicks",  "Impressions")
data.1$ratio  <-  ifelse(data.1$Impressions  ==  0,  0,  data.1$Clicks * 100/ data.1$Impressions)
data.1$ratio  <-  round(data.1$ratio,  2)
data.1  <-  data.1[,  -c(3,4)]
data.1a  <-  data.1[data.1$Brand_Guarantee  ==  1,  ]
data.1b  <-  data.1[data.1$Brand_Guarantee  ==  0,  ]
data.1  <-  cbind(data.1a,  data.1b)  ;  data.1  <-  data.1[,  -c(2,4,5)]
names(data.1)[2:3]  <-  c("With_BG",  "Without_BG")   
data.1$gap  <-  data.1$With_BG  -  data.1$Without_BG  
data.1  <-  data.1[order(data.1$gap),  ]

#plot
a1  <-  list(title  =  "(Click/Viewed_Impressions) %",  titlefont  =  f1,  showticklabels  =  TRUE
             ,  tickfont  =  f2)
a2  <-  list(title  =  "Country",  titlefont  =  f1,  tickfont  =  f2)

plot_ly(data.1,  x  =  With_BG,  y  =  Country,  name  =  "With BG",  mode  =  "markers"
      ,  marker  =  list(color  =  "Blue",  size  =  12))   %>%  add_trace(x  =  Without_BG
      ,  name  =  "Without BG", marker  =  list(color  =  "Orange",  size  =  12))  %>%  layout(xaxis  =  a1
,  yaxis  =  a2,  showlegend  =  TRUE) %>% layout(autosize  =  F,  width  =  1000
                          ,  height  =  500,  margin  =  m)
```
```
Observations:
    1. 'FR' (France) has the highest click rate across all geographies once Brand guarantee
    gets into action
    2. 'ES' witnessed the largest difference in click rate before (orange) & after(blue) 
    Brand guarantee
```

************
#Country wise (Views + Shares/visible impressions) percentage conditioned on Brand Guarantee (BG)
```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
data.2a  <-  aggregate(big.data$ViewsplusShares,  by  =  list(big.data$COUNTRY,  big.data$GUARANTEED_BRAND_SAFE),  sum)
data.2b  <-  aggregate(big.data$VISIBLE_IMPRESSIONS
            ,  by  =  list(big.data$COUNTRY,  big.data$GUARANTEED_BRAND_SAFE),  sum)
data.2  <-  merge(data.2a,  data.2b,  by  =  c("Group.1","Group.2"))
names(data.2)  <-  c("Country",  "Brand_Guarantee",  "SharesplusViews",  "Impressions")
data.2$Brand_Guarantee  <-  ifelse(data.2$Brand_Guarantee  ==  1,  "With BG",  "Without BG")
data.2$ratio  <-  ifelse(data.2$Impressions  ==  0,  0,  data.2$SharesplusViews * 100/ data.2$Impressions)
data.2$ratio  <-  round(data.2$ratio,  2)
data.2  <-  data.2[order(data.2$ratio),  ]

#plot
a1  <-  list(title  =  "Country",  titlefont  =  f1,  showticklabels  =  TRUE,  tickfont  =  f2)
a2  <-  list(title  =  "(Views + Shares)/Viewed_Impressions  %",  titlefont  =  f1,  tickfont  =  f2)

plot_ly(data.2,  x  =  Country,  y  =  ratio,  symbol  =  Brand_Guarantee
        , colors = "PuOr",  mode  =  "markers",  marker  =  list(size  =  12))  %>% layout(xaxis  =  a1
,  yaxis  =  a2,  showlegend  =  TRUE) %>% layout(autosize  =  F,  width  =  1000
,  height  =  500,  margin  =  m)
```
```
Observations:
    1. Only North American countries ('US', 'CA') have a significant (Views + Shares) rate
    2. The trend is counter intutive in the above 2 countries, as (View + Shares) rate has decreased 
    under the presence of brand guarantee
```

**********************
#Device Category wise Filled pages rate % (Filled Pages/ Total Impressions) by Post location
```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
data.3a  <-  aggregate(big.data$FILLED_PAGES,  by  =  list(big.data$DEVICE_CATEGORY
                                      ,  big.data$LOCATION_TYPE),  sum)
data.3b  <-  aggregate(big.data$TOTAL_IMPRESSION_REQUESTS,  by  =  list(big.data$DEVICE_CATEGORY,  big.data$LOCATION_TYPE),  sum)
data.3  <-  merge(data.3a,  data.3b,  by  =  c("Group.1","Group.2"))
names(data.3)  <-  c("DEVICE",  "LOCATION",  "Filled_Pages",  "TOTAL_Impressions")
data.3$ratio  <-  ifelse(data.3$TOTAL_Impressions  ==  0,  0,  data.3$Filled_Pages * 100/ data.3$TOTAL_Impressions)
data.3$ratio  <-  round(data.3$ratio,  2)

#plot
a1  <-  list(title  =  'LOCATION OF POST',  titlefont  =  f1,  showticklabels  =  TRUE,
             tickangle  =  0,  tickfont  =  f2)
a2  <-  list(title  =  "(Filled Page/Total_Impressions_Requests) %",  titlefont  =  f1)

plot_ly(data  =  data.3,  x  =  LOCATION,  y  =  ratio,  type  =  "bar"
,  color  =  DEVICE)  %>% layout(xaxis  =  a1,  yaxis  =  a2
,  margin  =  m)  %>%  layout(autosize  =  F,  width  =  1000,  height  =  500)
```
```
Observations:
    1. Filled Page rate is similar for all location types for any device
    2. Average Filled Page rate has been nearly 23% on the whole
```

************
#Device Category wise (Views + Shares/ Visible Impressions) % by Post location
```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
data.4a  <-  aggregate(big.data$ViewsplusShares,  by  =  list(big.data$DEVICE_CATEGORY
                                      ,  big.data$LOCATION_TYPE),  sum)
data.4b  <-  aggregate(big.data$VISIBLE_IMPRESSIONS,  by  =  list(big.data$DEVICE_CATEGORY,  big.data$LOCATION_TYPE),  sum)
data.4  <-  merge(data.4a,  data.4b,  by  =  c("Group.1","Group.2"))
names(data.4)  <-  c("DEVICE",  "LOCATION",  "Views_Shares",  "V_Impressions")
data.4$ratio  <-  ifelse(data.4$V_Impressions  ==  0,  0,  data.4$Views_Shares * 100/ data.4$V_Impressions)
data.4$ratio  <-  round(data.4$ratio,  2)

#plot
a1  <-  list(title  =  'LOCATION OF POST',  titlefont  =  f1,  showticklabels  =  TRUE,
             tickangle  =  0,  tickfont  =  f2)
a2  <-  list(title  =  "(View + Shares) %",  titlefont  =  f1)

plot_ly(data.4,  x  =  LOCATION,  y  =  ratio,  text  =  paste("Phase: ", DEVICE),
        mode  =  "markers",  color  =  DEVICE,  size  =  ratio/4) %>% layout(xaxis  =  a1
,  yaxis  =  a2,  showlegend  =  TRUE) %>% layout(autosize  =  F,  width  =  1000
,  height  =  500,  margin  =  m)
```
```
observations:
    1. 'Tablets' have the highest (Views + Shares) rate amongst the devices
    2. 'Other' has the highest (Views + Shares) rate amongst all locations
```

************
#Dispersion of Mean Total Impressions requests and mean Impressions for each publisher device wise
```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
data.6a  <-  aggregate(big.data$TOTAL_IMPRESSION_REQUESTS,  by  =  list(big.data$PLACEMENT_KEY
                                              ,  big.data$DEVICE_CATEGORY),  mean)
data.6b  <-  aggregate(big.data$IMPRESSIONS,  by  =  list(big.data$PLACEMENT_KEY
                                      ,  big.data$DEVICE_CATEGORY),  mean)
data.6  <-  merge(data.6a,  data.6b,  by  =  c("Group.1","Group.2"))
names(data.6)  <-  c("PLACEMENT_KEY","DEVICE","T_IMPRESSIONS","IMPRESSIONS")

#plot
a1  <-  list(title  =  'Mean Total Impressions requests for each post \t\t\t\t\t'
             ,  titlefont  =  f1,  showticklabels  =  TRUE,  tickangle  =  0,  tickfont  =  f2)
a2  <-  list(title  =  "Mean Impressions for each post",  titlefont  =  f1,  tickfont  =  f2)

plot_ly(data.6,  x  =  IMPRESSIONS,  y  =  T_IMPRESSIONS,  type  =  "scattergl",  mode  =  "markers"
,  color  =  DEVICE,  marker  =  list(size  =  12)) %>% layout(xaxis  =  a1,  yaxis  =  a2
,  showlegend  =  TRUE) %>% layout(autosize  =  F,  width  =  1000,  height  =  700,  margin  =  m)
cat("\n\n\n\n")
```
***************

```{r,  eval  =  TRUE,  echo  =  FALSE,  warning  =  FALSE}
cat(".\n.\n.\n.\n.\n.\n.\n.\n.\n")
cat("We witness a linear dependency between the mean of Total Impression requests and Impressions. So 
let us quantify the correlation between these 2 quantities and the significance between the 2 quantities,
using a simple Correlation test")
cor.test(data.6$T_IMPRESSIONS,  data.6$IMPRESSIONS)
cat("The test proves, that there is a significant corrrelation between Total Impression requests & Impressions.
Their correlation is .873.")
```



```{r,  echo  =  FALSE,  warning  =  FALSE,  message  =  FALSE}
#-----------------#  Clearing the environment ----#---------------------
#unloading all the packages 
detach("package:Hmisc",  unload  =  TRUE)
detach("package:plotly",  unload  =  TRUE)
detach("package:doMC",  unload  =  TRUE)
#Removing all the objects too
rm(list  =  ls())
```