---
title: '**Visualization_Completed_post_Jun_15**'
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 2
  pdf_document:
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_depth: 2
  word_document: default
---

```{r,  echo  =  FALSE,  results  =  'hide',  message  =  FALSE,  warning  =  FALSE}
#loading the libraries
library(plyr)  ;  library(sqldf)  ;  library(ggplot2)  ;  library(scales)
library(lubridate)  ;  library(bizdays)  ;  library(plotly)
```

```{r,  echo  =  FALSE,  results  =  'hide',  message  =  FALSE,  warning  =  FALSE}
#laoding the datasets
Project_milestone  <-  read.csv("~/Desktop/courses/PAST/Practicum1/Datasets/Sunrun/WFM_Project_Milestone_Dates.csv")  
Project_Attributes  <-  read.csv("~/Desktop/courses/PAST/Practicum1/Datasets/Sunrun/Project_Attributes copy.csv")
Project_Attributes  <-  Project_Attributes[  ,  -c(15:16)]

#Creating aliases
PM  <-  Project_milestone  ;  PA  <-  Project_Attributes  ; rm(Project_Attributes,Project_milestone)

#removing duplicates from both the dataset
PM  <-  PM[!duplicated(PM$Project.Name), ]  ;  PA  <-  PA[!duplicated(PA$Project.Name), ]   

#changing to suitable names
names(PA)  <-  c("Project.Name","Status","Purchased.through","Contract.type",
"Install.Branch","Utility","jurisdiction","Muncipality","System.size","If_build",
"if_MPU","If_Re_roof","If_HOA","If_PEStamp")

#Completion dates data
WC  <-  read.csv("~/Desktop/courses/PAST/Practicum1/Datasets/Sunrun/WFM_Completion_Dates.csv")
attach(WC)  
data  <-  WC[,c("Phase.Name",  "Workflow.Task.Name")]
names(data)  <-  c("Phase",  "Task")  ;  detach(WC)
#aggregating the bad.data to clean it
data.1  <-  sqldf("select Task,  Phase,  count(*) cnt from data group by Task,  Phase")
data.2  <-  data.1[order(-data.1$cnt),  ]#descending order, Task
#removing misclassified tasks out
data.3  <-  data.2[!duplicated(data.2$Task), ]  
#removing "Tasks" with too little counts (less than equal to 500 steps)
data.4  <-  data.3[data.3$cnt  >  500,  ]
data.4  <-  data.4[,  -3]
#total counts lost as percentage
sum(data.3$cnt[data.3$cnt  <=  500])  *  100 /  sum(data.3$cnt) #4.2% thats okay
#mapping the resulatant to the original dataset
names(WC)[2 :  3]  <-  c("old.Phase",  "Task")

#join using the "plyr" package
good.WC   <-  join(WC,  data.4,  by = "Task",  type  =  "inner",  match  =  "all")
#Using the correct phase information
good.WC  <-  good.WC[  ,  -c(2,  6)]

#Correcting column names
good.WC$Phase  <-  as.character(good.WC$Phase)
good.WC$Phase[good.WC$Phase  ==  "Project Initiation"]  <-  "1. Initiation"
good.WC$Phase[good.WC$Phase  ==  "Site Audit"]  <-  "2. Audit"
good.WC$Phase[good.WC$Phase  ==  "Contract Approval"]  <-  "3. Approval"
good.WC$Phase[good.WC$Phase  ==  "Design"]  <-  "4. Design"
good.WC$Phase[good.WC$Phase  ==  "Pre-Installation Approvals"]  <-  "5. Pre-Installation"
good.WC$Phase[good.WC$Phase  ==  "Installation"]  <-  "6. Installation"
good.WC$Phase[good.WC$Phase  ==  "Completion"]  <-  "7. Completion"

#Treating dates
good.WC$Start.Date  <-  as.Date(good.WC$Start.Date,  format = "%m/%d/%y %H:%M")
good.WC$End.Date  <-  as.Date(good.WC$End.Date,  format = "%m/%d/%y %H:%M")
#Excluding Holidays & Sundays
cal  <-  Calendar(holidaysANBIMA,  weekdays  =  'sunday')
#Days with Both Start Dates & End dates
good.WC  <-  good.WC[!is.na(good.WC$Task),]
#Goodsubset
good.WC  <-  good.WC[good.WC$Start.Date  >=  '2015-06-15',]
data  <-  good.WC[!is.na(good.WC$Start.Date) & !is.na(good.WC$End.Date),  ]
#Days with Start Dates less than Equal to End dates
data.new  <-  data[data$Start.Date  <=  data$End.Date,  ]
data.new$day.diff  <-  bizdays(data.new$Start.Date,  data.new$End.Date,  cal)
data.new  <-  data.new[data.new$Start.Date  >=  '2015-06-15',]

#Joining with the Project Attributes table to Get Project level details
complete.data  <-  join(data.new,  PA,  by  =  "Project.Name"
                        ,  type  =  "inner",  match  =  "all") 

#Sorting the other dataset
data.new  <-  data.new[order(-data.new$day.diff),]
data.new  <-  data.new[-1,]
phases  <-  unique(data.new$Phase)  ;  phases  <-  phases[order(phases)]

#Picking the rows Which have been completed
names(PM)[35]  <-  "End.date" #changing the name of the End date column
#Completed projects
Projects  <-  PM[!(is.na(PM$End.date)  |  PM$End.date  ==  ""),  c(1,  3)]
names(Projects)  <-  c("Project.Name",  "Project.Start.Date")
Projects  <-  na.omit(Projects) #Removing Projects with Junk names

#Selecting Only those projects that have been started after 14th June
Projects$Project.Start.Date  <-  as.Date(Projects$Project.Start.Date
                                         ,  format = "%m/%d/%y %H:%M")
Projects  <-  data.frame(Projects[Projects$Project.Start.Date >=  "2015-06-15",  1])
names(Projects)  <-  "Project.Name"  

#Analysis based on Start Dates
names(PM)[3]  <-  "Project.Start.Date" #changing the name of the End date column
#Completed projects
Projects.S  <-  PM[!(is.na(PM$Project.Start.Date)  |  PM$Project.Start.Date  ==  ""),  c(1,  3)]
names(Projects.S)  <-  c("Project.Name",  "Project.Start.Date")
Projects.S  <-  na.omit(Projects.S) #Removing Projects with Junk names

#Selecting Only those projects that have been started after 14th June
Projects.S$Project.Start.Date  <-  as.Date(Projects.S$Project.Start.Date
                                         ,  format = "%m/%d/%y %H:%M")
#7348 Started before "15th June, 2015"
#17966 Started on & after "15th June, 2015"
#Subsetting data for completion
complete.data  <-  join(complete.data,  Projects,  by  =  "Project.Name"
                        ,  type  =  "inner",  match  =  "all") 
data.new  <-  join(data.new,  Projects,  by  =  "Project.Name"
                        ,  type  =  "inner",  match  =  "all") 
good.WC  <-  join(good.WC,  Projects,  by  =  "Project.Name"
                        ,  type  =  "inner",  match  =  "all")
good.WC  <-  na.omit(good.WC)  ;  data.new  <-  na.omit(data.new)

#plotly styling
f1  <-  list(family  =  "Arial, sans-serif",  size  =  20,  color  =  "brown")
f2  <-  list(family  =  "Arial, sans-serif",  size  =  16,  color  =  "blue")
f3  <-  list(family  =  "Arial, sans-serif",  size  =  12,  color  =  "blue")
m  <-  list( l  =  50,  r  =  50,  b  =  50,  t  =  50,  pad  =  4) #Setting margin
```

************

# Number of Ongoing projects per phase

```{r,  echo  =  FALSE,  warning  =  NA}
m  <-  unique(good.WC[,  c(1,5)])
Phase.count  <-  aggregate(m$Phase,  by  =  list(m$Project.Name),  length)
names(Phase.count)  <-  c("Project",  "count")
phase.data  <-  aggregate(Phase.count$Project,  by  =  list(Phase.count$count)
                          ,  length)
names(phase.data)  <-  c("Phases",  "Frequency")
phase.data$Frequency  <-  phase.data$Frequency/1000

#Styling
a1  <-  list(autotick  =  FALSE,  ticks  =  "outside",  tick0  =  1,  dtick  =  1,
           ticklen  =  7,  tickwidth  =  2,  tickcolor  =  toRGB("blue")
           ,  title  =  "Phases",  titlefont  =  f1)
a2  <-  list(title  =  "Number of Projects ('000) \n",  titlefont  =  f1)

#Boxplot for the data
plot_ly(x  =  Phases,  y  =  Frequency,  name  =  "Number of Projects on each phase"
        ,  type  =  "bar",  data  =  phase.data) %>% layout(xaxis  =  a1,
                                                            yaxis  =  a2)
```

*******************

# Number of steps completed and the number of projects

```{r,  echo  =  FALSE,  warning  =  NA}
m1  <-  aggregate(good.WC$Task,  by  =  list(good.WC$Project.Name),  length)
names(m1)  <-  c("Project",  "count")
#checking out the plot for each project & number of steps involved
q  <-  ggplot(data  =  m1,  aes(x  =  count,  fill  =  "blue"))  
q  <-  q  +  geom_histogram(binwidth  =  1,  color  =  "black")
q  <-  q  +  theme_bw()  +  xlab("\n Number of steps completed")
q  <-  q  +  ylab("Number of projects \n")  +   guides(fill  =  FALSE)
q  <-  q  +  ggtitle("Frequency distribution of projects & steps")
q  <-  q  +  scale_x_continuous(breaks  =  seq(1,  49,  2))
q  <-  q  +  scale_y_continuous(labels  =  comma)
q  <-  q  +  theme(
  axis.title  =  element_text(size  =  20,  color  =  "brown",  face  =  "bold"),
  axis.title.y  =  element_text(vjust  =  1)
)
q
```

*******************
# Average time taken per step per phase 

```
Days taken for each phase excluding Sundays and US holidays.
```

```{r,  echo  =  FALSE,  warning  =  NA}
#Plot for Average number of steps involved per phase
m3  <-  aggregate(data.new$day.diff,  by  =  list(data.new$Phase),  mean)
names(m3)  <-  c("Phase",  "Avg.days")
#Sorting as per the exceution order
m3   <-  m3[c(6,2,7,3,5,4,1),]   ;  row.names(m3)  <-  c(1:7)

g3  <-  ggplot(data  =  m3,  aes(x  =  Phase,  y  =  Avg.days,  fill  =  Phase)) 
g3  <-  g3  +  geom_bar(colour  =  "black",  stat  =  "identity")  
g3  <-  g3  +  guides(fill  =  FALSE)  
g3  <-  g3  +  ggtitle("Avg days per phase per step")
g3  <-  g3  +  labs(x  =  "\n Phases",  y  =  "\n Days") 
g3  <-  g3  +  theme(
  axis.title  =  element_text(size  =  20,  color  =  "brown",  face  =  "bold"),
  axis.title.y  =  element_text(vjust  =  2))
g3  +  theme(axis.text.x  =  element_text(angle  =  10,  hjust  =  1))

#Box plot for the data
a1  <-  list(title  =  "Phase",  titlefont  =  f1,  showticklabels  =  TRUE,
  tickangle  =  0,  tickfont  =  f2)
a2  <-  list(title  =  "Days",  titlefont  =  f1)
data.new  <-  data.new[order(data.new$Phase),]

#Box plot for the data
plot_ly(data.new,  x  =  Phase,  y  =  day.diff,  type  =  "box") %>% layout(xaxis  =  a1
                      ,  yaxis  =  a2,  showlegend  =  FALSE,  autorange  =  'reversed') %>% layout(autosize  =  F
,  width  =  1000,  height  =  500,  margin  =  m)
```
All phases have plenty of outliers, skewing the distribution of average days per phase.

*******************

# Average days taken per step per phase Installation branch wise

```{r,  echo  =  FALSE,  message  =  FALSE,  warning  =  FALSE}
#Subsetting data of interest
cols  <-  c("Install.Branch","day.diff","Phase")
p4  <-  complete.data[,  cols]
plot4  <-  aggregate(p4$day.diff,  by  =  list(p4$Install.Branch,  p4$Phase),  mean)
names(plot4)  <-  c("Install.Branch",  "Phase",  "Avg.Days")

#plot
a1  <-  list(title  =  "Phase",  titlefont  =  f1,  showticklabels  =  TRUE,
  tickangle  =  0,  tickfont  =  f2)
a2  <-  list(title  =  "Days",  titlefont  =  f1)

plot_ly(plot4,  x  =  phases,  y  =  Avg.Days,  text  =  paste("Phase: ", Phase),
        mode  =  "markers",  color  =  Install.Branch,  size  =  Avg.Days) %>% layout(xaxis  =  a1
,  yaxis  =  a2,  showlegend  =  TRUE) %>% layout(autosize  =  F,  width  =  1100
,  height  =  500,  margin  =  m)
```

*******************

# Average days taken per step per phase by contract type

```{r,  echo  =  FALSE,  warning  =  NA}
#Subsetting data of interest
cols  <-  c("Contract.type","day.diff","Phase")
p5  <-  complete.data[,  cols]
plot5  <-  aggregate(p5$day.diff,  by  =  list(p5$Contract.type,  p5$Phase),  mean)
names(plot5)  <-  c("Contract.type",  "Phase",  "Avg.Days")

#Changing the names of Contract to more appopriate
plot5  <-  within(plot5,  levels(Contract.type)
[levels(Contract.type)  ==  "Custom PPA Fixed"] <-  "PPA")
plot5  <-  within(plot5,  levels(Contract.type)
[levels(Contract.type)  ==  "Custom Lease"] <-  "Lease")
plot5  <-  within(plot5,  levels(Contract.type)
[levels(Contract.type)  ==  "Customer Owned - Bank Financed"] <-  "Financed")
plot5  <-  within(plot5,  levels(Contract.type)
[levels(Contract.type)  ==  "Customer Owned - Full Upfront"] <-  "Full.Upfront")
plot5  <-  within(plot5,  levels(Contract.type)
[levels(Contract.type)  ==  "Low Upfront Lease"] <-  "Low.Upfront")
plot5  <-  within(plot5,  levels(Contract.type)
[levels(Contract.type)  ==  "Low Upfront"] <-  "Low.Upfront")
plot5  <-  within(plot5,  levels(Contract.type)
[levels(Contract.type)  ==  "Low Upfront PPA Fixed"] <-  "Low.Upfront.PPA")
plot5  <-  plot5[plot5$Contract.type  !=  "",  ]  #Removing Missing values

#plot
a1  <-  list(title  =  "Contract Type",  titlefont  =  f1,  showticklabels  =  TRUE
             ,tickangle  =  10,  tickfont  =  f3)
a2  <-  list(title  =  "Days",  titlefont  =  f1)

plot_ly(plot5,  x  =  Contract.type,  y  =  Avg.Days,  symbol  =  Phase
        , colors = "PuOr",  mode  =  "markers")  %>% layout(xaxis  =  a1
,  yaxis  =  a2,  showlegend  =  TRUE) %>% layout(autosize  =  F,  width  =  1000
,  height  =  500,  margin  =  m)
```

*******************

# Avg days taken per step for projects

```{r,  echo  =  FALSE,  warning  =  NA}
#Subsetting data of interest
cols  <-  c("Project.Name","day.diff","Phase")
p6  <-  complete.data[,  cols]
plot6  <-  aggregate(p6$day.diff,  by  =  list(p6$Project.Name,  p6$Phase),  mean)
names(plot6)  <-  c("Project","Phase","avg.days")
#aggregrating the data again
plot6  <-  aggregate(plot6$avg.days,  by  =  list(plot6$Project),  mean)
names(plot6)  <-  c("Project","Avg.duration")

#Treating Outliers : [0, 15] Fixing Range
plot6[plot6$Avg.duration  >  15,  2]  <-  15
plot6[plot6$Avg.duration  <  0,  2]  <-  0

g6  <-  ggplot(plot6,  aes(x  =  Avg.duration)) 
g6  <-  g6  +  geom_histogram(color  =  "black",  fill  =  "lightblue",  binwidth  =  1)  
g6  <-  g6  +  ggtitle("Frequency distribution of Avg time taken per step")  
g6  <-  g6  +  xlab("\n Avg duration for each step (days)")
g6  <-  g6  +  ylab("Frequency of Projects \n")
g6  <-  g6  +  theme(axis.text  =  element_text(size  =  12)
        ,  axis.title  =  element_text(size  =  16,  face  =  "bold"))
g6  <-  g6  +  scale_y_continuous(labels  =  comma)
g6  +  theme(
  axis.title  =  element_text(size  =  20,  color  =  "brown",  face  =  "bold"),
  axis.title.y  =  element_text(vjust  =  1)
)
```

*******************

# Average days taken per step for each phase conditioned on Re-Roofing

```{r,  echo  =  FALSE,  warning  =  NA}
cols  <-  c("If_Re_roof","day.diff","Phase")
p8  <-  complete.data[,  cols]
plot8  <-  aggregate(p8$day.diff,  by  =  list(p8$If_Re_roof,  p8$Phase),  mean)
names(plot8)  <-  c("If_Re_roof",  "Phase",  "Avg.Days")

plot8$If_Re_roof  <-  ifelse(plot8$If_Re_roof  ==  "1",  "With Re-Roof",  "Without Re-Roof")

#plot
a1  <-  list(title  =  "Phase",  titlefont  =  f1,  showticklabels  =  TRUE
             ,  tickfont  =  f2,  tickangle  =  0)
a2  <-  list(title  =  "Days",  titlefont  =  f1)

plot_ly(plot8,  x  =  Phase,  y  =  Avg.Days,  symbol  =  If_Re_roof 
        , colors = "PuOr",  mode  =  "markers",  marker  =  list(size  =  15)) %>% layout(xaxis  =  a1
,  yaxis  =  a2,  showlegend  =  TRUE) %>% layout(autosize  =  F,  width  =  1100
,  height  =  500,  margin  =  m)
```

*******************

# Average days taken per step for each phase conditoned on Home-Owner's Association (HOA)

```{r,  echo  =  FALSE,  warning  =  NA}
cols  <-  c("If_HOA","day.diff","Phase")
p9  <-  complete.data[,  cols]  ;  p9$If_HOA[p9$If_HOA  ==  "2"]  <-  "1"
plot9  <-  aggregate(p9$day.diff,  by  =  list(p9$If_HOA,  p9$Phase),  mean)
names(plot9)  <-  c("If_HOA",  "Phase",  "Avg.Days")
plot9$If_HOA  <-  ifelse(plot9$If_HOA  ==  "1",  "With HOA",  "Without HOA")

#plot
a1  <-  list(title  =  "Phase",  titlefont  =  f1,  showticklabels  =  TRUE
             ,  tickfont  =  f2)
a2  <-  list(title  =  "Days",  titlefont  =  f1)

plot_ly(plot9,  x  =  Phase,  y  =  Avg.Days,  symbol  =  If_HOA,  colors  =  "PuOr"
,  mode  =  "markers",  marker  =  list(size  =  15)) %>% layout(xaxis  =  a1
,  yaxis  =  a2,  showlegend  =  TRUE) %>% layout(autosize  =  F,  width  =  1050
,  height  =  500,  margin  =  m)
```

*******************
# Average days taken per step for each phase conditioned on External Build Partners (BP)

```{r,  echo  =  FALSE,  warning  =  NA}
cols  <-  c("If_build","day.diff","Phase")
p10  <-  complete.data[,  cols]
plot10  <-  aggregate(p10$day.diff,  by  =  list(p10$If_build,  p10$Phase),  mean)
names(plot10)  <-  c("If_build",  "Phase",  "Avg.Days")
plot10$If_build  <-  ifelse(plot10$If_build  ==  "1",  "With BP",  "without BP")

#plot
a1  <-  list(title  =  "Phase",  titlefont  =  f1,  showticklabels  =  TRUE
             ,  tickfont  =  f2)
a2  <-  list(title  =  "Days",  titlefont  =  f1,  showticklabels  =  TRUE,
      tickfont  =  f2)

plot_ly(plot10,  x  =  Phase,  y  =  Avg.Days,  symbol  =  If_build,  colors  =  "PuOr"
,  mode  =  "markers",  marker  =  list(size  =  15)) %>% layout(xaxis  =  a1,  yaxis  =  a2
,  showlegend  =  TRUE) %>% layout(autosize  =  F,  width  =  1050,  height  =  500,  margin  =  m)
```

*******************
# Average days taken per step for each phase conditioned on Professional Engineer's (PE) Stamp Approval

```{r,  echo  =  FALSE,  warning  =  NA}
cols  <-  c("If_PEStamp","day.diff","Phase")
p11  <-  complete.data[,  cols]
plot11  <-  aggregate(p11$day.diff,  by  =  list(p11$If_PEStamp,  p11$Phase),  mean)
names(plot11)  <-  c("If_PEStamp",  "Phase",  "Avg.Days")
plot11$If_PEStamp  <-  ifelse(plot11$If_PEStamp  ==  "1",  "With PE_Stamp",  "Without PE_Stamp")

#plot
a1  <-  list(title  =  "Phase",  titlefont  =  f1,  showticklabels  =  TRUE
             ,  tickfont  =  f2,  tickangle  =  0)
a2  <-  list(title  =  "Days",  titlefont  =  f1,  showticklabels  =  TRUE,
      tickfont  =  f2)

plot_ly(plot11,  x  =  Phase,  y  =  Avg.Days,  symbol  =  If_PEStamp 
, colors = "PuOr",  mode  =  "markers",  marker  =  list(size  =  15)) %>% layout(xaxis  =  a1
,  yaxis  =  a2,  showlegend  =  TRUE) %>% layout(autosize  =  F
,  width  =  1050,  height  =  500,  margin  =  m)
```

*******************
# Average days taken per step for each phase conditioned on Main Panel Upgrade(MPU)  

```{r,  echo  =  FALSE,  warning  =  NA}
cols  <-  c("if_MPU","day.diff","Phase")
p12  <-  complete.data[,  cols]
plot12  <-  aggregate(p12$day.diff,  by  =  list(p12$if_MPU,  p12$Phase),  mean)
names(plot12)  <-  c("if_MPU",  "Phase",  "Avg.Days")
plot12$if_MPU  <-  ifelse(plot12$if_MPU  ==  "1",  "With MPU",  "Without MPU")

#plot
a1  <-  list(title  =  "Phase",  titlefont  =  f1,  showticklabels  =  TRUE
             ,  tickfont  =  f2,  tickangle  =  0)
a2  <-  list(title  =  "Days",  titlefont  =  f1,  showticklabels  =  TRUE,
      tickfont  =  f2)

plot_ly(plot12,  x  =  Phase,  y  =  Avg.Days,  symbol  =  if_MPU,  colors  =  "PuOr"
        ,  mode  =  "markers",  marker  =  list(size  =  15)) %>% layout(xaxis  =  a1,  yaxis  =  a2
,  showlegend  =  TRUE)  %>% layout(autosize  =  F,  width  =  1050,  height  =  500,  margin  =  m)
```

**************************************
# Last Project Status on average days taken per step for each phase 

```{r,  echo  =  FALSE,  warning  =  NA}
cols  <-  c("Status","day.diff","Phase")
p13  <-  complete.data[,  cols]
plot13  <-  aggregate(p13$day.diff,  by  =  list(p13$Status,  p13$Phase),  mean)
names(plot13)  <-  c("Status",  "Phase",  "Avg.Days")

#plot
a1  <-  list(title  =  "Phase",  titlefont  =  f1,  showticklabels  =  TRUE
             ,  tickfont  =  f2)
a2  <-  list(title  =  "Days",  titlefont  =  f1,  showticklabels  =  TRUE,
      tickfont  =  f2)

plot_ly(plot13,  x  =  Phase,  y  =  Avg.Days,  symbol  =  Status ,  colors  =  "PuOr"
,  mode  =  "markers",  marker  =  list(size  =  15))  %>%  layout(xaxis  =  a1,  yaxis  =  a2
,  showlegend  =  TRUE) %>% layout(autosize  =  F,  width  =  1050,  height  =  500,  margin  =  m)
```

**************************************
# Average % of projects completed Vs number of days passed

```{r,  echo  =  FALSE,  warning  =  NA}
data2  <-  data.new  ;  rm(data.new)
names(data2)  <-  c('Project','Task','Start','End','Phase','days')
n  <-  sqldf("select Project, (max(End) - min(Start)) Days from data2 group by Project")
names(n)  <-  c('Project','Days')

n.1  <-  data.frame(table(n$Days))  #Creating a Frequency table
n.1$prop  <-  cumsum(n.1$Freq)  *  100  /  sum(n.1$Freq)
n.1$prop  <-  as.integer(n.1$prop)  ;  names(n.1)[1]  <-  "Days"  

#plot
a1  <-  list(title  =  "Days",  titlefont  =  f1,  showticklabels  =  TRUE
             ,  tickfont  =  f2)
a2  <-  list(title  =  "% Completed",  titlefont  =  f1,  showticklabels  =  TRUE,
      tickfont  =  f2)

plot_ly(data  =  n.1,  x  =  Days,  y  =  prop,  colors  =  "PuOr",  mode  =  "markers") %>%  layout(xaxis  =  a1,  yaxis  =  a2,  showlegend  =  FALSE) %>% layout(autosize  =  F,  width  =  700,  height  =  500,  margin  =  m)
```

**************************************

```{r,  echo  =  FALSE,  eval  =  FALSE,  warning  =  NA}
# Extent of Overlap in the dataset (Analysis in Code)
m  <-  sqldf("select Project, Phase, (max(End) - min(Start)) Days from data2 group by Project, Phase")
names(m)  <-  c('Project','Phase','Days')

#Now rolling it up to Project level from Individual phases of projects
m.agg  <-  aggregate(m$Days,  by  =  list(m$Project),  sum)  
names(m.agg)  <-  c("Project","Days")

#Combing the above 2 tables to get the overlap on Project level
project.days  <-  merge(n,  m.agg,  by  =  'Project',  all  =  TRUE) 
names(project.days)[2:3]  <-  c('Overall_days','Phases_days')
#guaging extent of Overlap between phases 
for  (i  in  1:length(project.days[,1]))  {
  project.days$Ratio[i]  <-  project.days$Phases_days[i]/project.days$Overall_days[i]
}

#Printing extent of Overlap within phases
cat("Extent of overlap within phases for completed projects on average has been",mean(project.days$Ratio))

#Exploring why there was the Overlap
m.1  <-  sqldf("select Project, Phase, min(Start) Start, max(End) End from data2  group by Project, Phase")
names(m.1)  <-  c('Project','Phase','Start','End')

#Going from long to short on the Dataframe
data.wide  <-  reshape(m.1,  timevar  =  "Phase",  idvar  =  "Project"
                       ,  direction  =  "wide")
#Naming cols appropriately
names(data.wide)[2:15]  <-  c('Initiate.S','Initiate.E','Audit.S','Audit.E'
,'Approve.S','Approve.E','Design.S','Design.E','Pre_Instal.S','Pre_Instal.E'
,'Install.S','Install.E','Complete.S','Complete.E')
```



```{r,  echo  =  FALSE,  results  =  'hide',  message  =  FALSE,  warning  =  FALSE}
#unloading all the packages
detach("package:sqldf",  unload  =  TRUE)
detach("package:lubridate",  unload  =  TRUE)
detach("package:bizdays",  unload  =  TRUE)
#Removing all the objects too
rm(list  =  ls())
```